### 2022-06-02 main/chapter_2ljets.tex
make an llbb command

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
\caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
\caption{SR-$\ell\ell bb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
\caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
\caption{SR-Low}
\end{subfigure}
\caption[
Example signal region histograms with benchmark signal sample yields overlaid
]{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines~\cite{atlas2022searches}.
Physically, signal yields would add on top of the backgrounds.
Data are shown; regions in the top two plots observe zero data, and
Poisson error bars for $0$ events are hidden for aesthetic reasons.
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lccrrcc}
Region &
\multicolumn{2}{c}{Fitted} &
Data &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
$S_{\mathrm{obs}}^{95}$ &
$S_{\mathrm{exp}}^{95}$ &
$\mathrm{CLb}$ &
$p(s=0)$ \\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$ \\[.5ex]
DR-Low & $22$ & $4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$ \\[.5ex]
DR-Int & $35$ & $4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$ \\[.5ex]
DR-High & $3.9$ & $0.5$ & 0 & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51$ & $0.20$ & 0 & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$ \\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\TODO{add labels and references to asymptotic formulae paper}
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[.5em]
\: VR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\subsubsection{\texorpdfstring{$\ell\ell bb$}{\textit{llbb}}}

@@

\begin{itemize}
\item DR-High: SR-High-8
\item DR-$\ell\ell bb$: SR-$\ell\ell bb$
\item DR-Int: SR-Int
\item DR-Low: SR-Low
\item DR-OffShell: SR-OffShell
\end{itemize}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_600.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_700.png}
\caption{}
\end{subfigure}
\caption[
Evaluation of candidate $\ell\ell bb$ discovery regions
]{%
Evaluation of candidate $\ell\ell bb$ discovery regions.
The region SR-$\ell\ell bb$, labelled `SRllbb' here, is chosen for
sensitivity, simplicity, and to avoid overlapping with DR-High.
Upper plots show background and signal yields.
Lower plots show various measures of projected
sensitivity~\cite{cousins2008evaluation}.
Yields are derived in an early iteration of the analysis and do not exactly
match those in the final result.
}
\label{fig:2ljets_disco_trials_llbb}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\ell\ell bb$}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions
]{%
Pre-fit yields in discovery regions.
Errors are statistical.
}
\label{fig:2ljets_disco_prefit}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
\caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
\caption{SR-$\llbb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
\caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
\caption{SR-Low}
\end{subfigure}
\caption[
Example signal region histograms with benchmark signal sample yields overlaid
]{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines~\cite{atlas2022searches}.
Physically, signal yields would add on top of the backgrounds.
Data are shown; regions in the top two plots observe zero data, and
Poisson error bars for $0$ events are hidden for aesthetic reasons.
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lccrrcc}
Region &
\multicolumn{2}{c}{Fitted} &
Data &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
$S_{\mathrm{obs}}^{95}$ &
$S_{\mathrm{exp}}^{95}$ &
$\mathrm{CLb}$ &
$p(s=0)$ \\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$ \\[.5ex]
DR-Low & $22$ & $4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$ \\[.5ex]
DR-Int & $35$ & $4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$ \\[.5ex]
DR-High & $3.9$ & $0.5$ & 0 & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50$ \\[.5ex]
DR-$\llbb$ & $0.51$ & $0.20$ & 0 & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$ \\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\TODO{add labels and references to asymptotic formulae paper}
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

\begin{table}[tp]
\centering
\begin{tabular}{lccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X$
& $\rjj$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj\!:~  60\textrm{--}110$
& $0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\: VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
& $< 1.6$
\\[.5em]
\: VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\uwave{\mjj\!:~  > 20}$
& $\uwave{> 1.6}$
\\[1em]
SR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone\!:~  60\textrm{--}110$
&
\\[.5em]
\: VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\uwave{\mjetone\!:~  20\textrm{--}60 \mid 60\textrm{--}110}$
&
\\[1em]
SR-$\llbb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb\!:~  60\textrm{--}150$
&
\\[.5em]
\: VR-$\llbb$
& $\geq 2$
& $\geq 2$
& $\uwave{12\textrm{--}18}$
& $\mbb\!:~  60\textrm{--}150$
&
\end{tabular}
\\[1em]
Common: Preselection,
$\mll \in 71\textrm{--}111$, and
$\mttwoll > 80$.
\caption[
High region definitions in the $\twoljets$-electroweak analysis
]{%
High region definitions in the $\twoljets$-electroweak analysis.
En-dashes `$a\textrm{--}b$' indicate open intervals $(a, b)$.
Concatenated intervals `$a\textrm{--}b\textrm{--}c$' indicate binning
with boundaries at $a$, $b$, and $c$.
The mid bar `$\mid$' indicates logical or.
Differences between regions are \uwave{underlined}.
}
\label{tab:2ljets_high}
\end{table}

@@

\subsubsection{\texorpdfstring{$\llbb$}{\textit{llbb}}}

@@

\begin{itemize}
\item DR-High: SR-High-8
\item DR-$\llbb$: SR-$\llbb$
\item DR-Int: SR-Int
\item DR-Low: SR-Low
\item DR-OffShell: SR-OffShell
\end{itemize}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_600.png}
\caption{}
\end{subfigure}
\hfill
\begin{subfigure}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_llbb_C1N2N1_GGMHinoZh50_700.png}
\caption{}
\end{subfigure}
\caption[
Evaluation of candidate $\llbb$ discovery regions
]{%
Evaluation of candidate $\llbb$ discovery regions.
The region SR-$\llbb$, labelled `SRllbb' here, is chosen for
sensitivity, simplicity, and to avoid overlapping with DR-High.
Upper plots show background and signal yields.
Lower plots show various measures of projected
sensitivity~\cite{cousins2008evaluation}.
Yields are derived in an early iteration of the analysis and do not exactly
match those in the final result.
}
\label{fig:2ljets_disco_trials_llbb}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRHigh.png}
\caption{DR-High}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRllbb.png}
\caption{DR-$\llbb$}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRInt.png}
\caption{DR-Int}
\end{subfigure}
\quad\quad
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DRLow.png}
\caption{DR-Low}
\end{subfigure}
\\[.5em]
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_disco_plot_DROffShell.png}
\caption{DR-OffShell}
\end{subfigure}
\caption[
Pre-fit yields in discovery regions
]{%
Pre-fit yields in discovery regions.
Errors are statistical.
}
\label{fig:2ljets_disco_prefit}
\end{figure}
